Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-06-13 emsoft-2019/V2/response.tex

Here, we provide answer to the main inquiries posed by the reviewers. These points will be added later into the main body of the final version of our paper.\\
\textbf{Significance of memory savings reported in the paper} (Reviewer 1)\\
Explicit MPC is a class of controllers which is mainly appropriate for implementation over processors with limited computational power as it omits the need for massive online optimizations. This speed up in execution comes however with relatively high memory demand due to high number of PWA mappings that must be saved over the memory. Typical memory of these processors is in the order of tens of kilobytes (e.g. $32$ KB) and hence $21$ KB is considered as a significant save.\\
\textbf{Do memory savings in our approach come with a run-time cost?} (Reviewer 1)\\
No. It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.\Rocco{On the other hand, mixed-precision naturally requires casting operators, which may potentially affect the running time.}\\

@@

\textbf{Taking uncertainties other than quantization into account} (Reviewer 1)\\
Our formulation is general enough to take the effect of measurement/process noise into account. More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources. However, this is not subject of study of the current paper.\\
\textbf{Complexity of the proposed approach} (Reviewer 2)\\
In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}. In theory one cannot find an upper bound for the maximum number of hyperplanes enclosing a region. To compute the incorrect region selection error, assuming that each partition at most has $\bar n_f$ faces, in the worst case $i\times\bar n_f\times 2^q$ affine computations would be enough, where $i$ denotes the number of times that RMPC design is repeated for updated $\Delta$s. In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks. %\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}} 		
\Rocco{The complexity of precision tuning is linear with respect to the number of regions and hyperplanes. So, $P+\bar n_f\times P$ is an upper bound for the number of problems we need to encode in Daisy.
In each encoding, the uniform-precision detection takes linear steps before convergence. It starts from 1-bit and increases the precision one by one until the first valid configuration. The complexity of mixed-precision tuning, with delta-debugging, is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with n number of variables.}\\

### 2019-06-14 emsoft-2019/V2/intro.tex
updates

One way to tackle these problems is through \emph{explicit MPC} (EMPC) \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
problem but computes offline a symbolic representation of the solution as a function of the state.
At run-time, the solution is evaluated on the current state as in conventional control.
For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
using multi-parametric programming techniques.
The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
and an affine map for each region. 
\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.

>>>>

One way to tackle these problems is through \emph{explicit MPC} (EMPC) \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
problem but computes offline a symbolic representation of the solution as a function of the state.
At run-time, the solution is evaluated on the current state as in conventional control.
For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
using multi-parametric programming techniques.
The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
and an affine map for each region. 
\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{perform massive online computations}
or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.
